Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2023-02-06 manuscript.Rmd
enable cross references for article

```{r, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "Posterior Probability (corroboration as firmness) as a function of $\tau$, where $\tau$ is either certain (solid line) or maximally uncertain (dotted line)."

@@

```{r, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "Several measures for corroboration as increase in firmness as a function of $\tau$, where $\tau$ is either certain (solid line) or maximally uncertain (dotted line)."

>>>>

```{r posterior-fig, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "\\label{fig:posterior}Posterior Probability (corroboration as firmness) as a function of $\\tau$, where $\\tau$ is either certain (solid line) or maximally uncertain (dotted line)."

@@

```{r other-measures-fig, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "\\label{fig:other-measures}Several measures for corroboration as increase in firmness as a function of $\\tau$, where $\\tau$ is either certain (solid line) or maximally uncertain (dotted line)."
